---
title: "p8105_hw1_fx2184"
author: "Fei"
output: github_document
---
```{r}
library(skimr)
library(tidyverse)

```

# Problem 1 

```{r, warning = FALSE, measage= FALSE}
data("penguins", package = "palmerpenguins") 

skim(penguins)
var_name = names(penguins)

# the dataset "penguins" contains 344 rows (observations), and 8 columns. 
# 8 variables are species, island, bill_length_mm, bill_depen_nm, body_mass_g, sex and year. 
nrow = nrow(penguins)
ncol = ncol(penguins)

# Mean of the flipper_length_mm
meaa_flipper_length_mm = mean(penguins$flipper_length_mm, na.rm=TRUE)

# Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x)
scatterplot = ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, col =species)) + geom_point()

# Export your first scatterplot to your project directory using ggsave.
ggsave("Scatterplot.pdf", plot = scatterplot)

```
The size of the dataset is `r nrow` x `r ncol`. <br>
The names of the variables are `r var_name`. <br>
The mean flipper length is `r meaa_flipper_length_mm`.

# Problem 2 

## Create a data frame 

```{r}
df_p2 = tibble(
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0,
  vec_char = rep(c("a", "b", "c", "d", "e"), length.out = 10),
  vec_factor = factor(rep(c("high","middle","low"), length.out = 10))
  )
```

## mean of the variable 

```{r, warning=FALSE, message=FALSE}
mean(pull(df_p2,vec_numeric))
mean(pull(df_p2,vec_logical))
mean(pull(df_p2,vec_char))
mean(pull(df_p2,vec_factor))
# R cannot calculate mean for vec_char and vec_factor variables. 
```

## convert variables

```{r,meassage=  FALSE,warning=FALSE}
mean(as.numeric((pull(df_p2,vec_logical))))
mean(as.numeric(pull(df_p2,vec_char)))
mean(as.numeric(pull(df_p2,vec_factor)))

```

The logical variable and factor variable are successfully converted to numeric variable, but the character variable cannot be converted. I think even using as.numeric function, the character variable till does not be signed as number, so it cannot calculate mean. However, the as.numeric function transform factor variable with certain level, so the mean can be calculated. 


